From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-20 paper.tex
Minor tweaks

\begin{figure}[t]
    \includegraphics[width=.45\columnwidth]{images/livre}\hfill
    \includegraphics[width=.45\columnwidth]{images/livreLOD}
  \caption{\label{fLivre}Livre rendering a MicroCT dataset (left) and
    the selected LODs (right)}
\end{figure}

@@

\section{Messaging and Service Architecture}

\begin{wrapfigure}{r}{.382\textwidth}\center\vspace{-6ex}
  \includegraphics[width=.382\textwidth]{images/ZeroMS}
  {\caption{\label{fZero}New messaging use cases}}\vspace{-6em}
\end{wrapfigure}

@@

while( rendering )
{
    subscriber.receive( 0 /*ms, poll*/ );
    updateCamera( camera );
    publisher.publish( camera );
    renderFrame( camera );
}
\end{lstlisting}

>>>>

\begin{figure}[t]
    \includegraphics[width=.49\columnwidth]{images/livre}\hfill
    \includegraphics[width=.49\columnwidth]{images/livreLOD}
  \caption{\label{fLivre}Livre rendering a MicroCT dataset (left) and
    the selected LODs (right)}
\end{figure}

@@

\clearpage
\section{Messaging and Service Architecture}

\begin{wrapfigure}{r}{.382\textwidth}\center\vspace{-6ex}
  \includegraphics[width=.382\textwidth]{images/ZeroMS}
  {\caption{\label{fZero}Messaging-enabled use cases}}\vspace{-1em}
\end{wrapfigure}

@@

while( rendering )
{
    if( updateCamera( camera )) // had user event
        publisher.publish( camera );
    else // poll subscription
        subscriber.receive( 0 /*ms*/ );
    renderFrame( camera );
}
\end{lstlisting}
